---
title: "ALFRESCO Data Extraction: Function Code"
output:
  html_document:
    toc: false
    theme: cosmo
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/alfresco/alfExtract.R")
```

## Introduction

The `alfExtract.R` script uses extract fire and vegetation statistics from calibrated, finalized ALFRESCO run output over the full Alaska-Canada 1-km resolution ALFRESCO extent.
Data are saved to **R** workspaces (.RData files) for analysis and graphing by subsequent **R** code.

### Details

This script is called by the wrapper script, `alfExtractMain.R` as part of a non-interactive **R** SLURM job process using `Rmpi`.
The script consists of functions, which are loaded onto each CPU core.
The execution calls still originate from the parent `Rpmi` script on the head node.

### Files and data

The input files include 1-km Alaska-Canada extent data from ALFRESCO simulations
as well as raster layer cell indices pertaining to various regional shapefile polygons.
All input data are passed directly from the `alfExtractMain.R` master **R** session running on the head node.
`alfExtract.R` performs data extractions on multiple CPU cores across multiple compute nodes based on the data passed down to each CPU.
Each CPU on the compute nodes is responsible for processing data for a unique ALFRESCO simulation spatial time series replicate.

`alfExtract.R` passed some computed ALFRESCO output statistics back to `alfExtractMain.R` on the head node to be combined, organized and written to intermediary files:

* Fire data (burn area, fire frequency and fire sizes) by region and vegetation class
* Vegetation age by region and vegetation class
* Vegetated area by region and vegetation class

## R code

### Setup

```{r setup}
```

### Processing functions

#### extract_data

```{r extract_data}
```

#### extract_fsv

```{r extract_fsv}
```

#### extract_av


```{r extract_av}
```
