---
title: ALFRESCO Data Prep
output:
  html_document:
    toc: false
    theme: cosmo
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/alfresco/alfPrep.R")
```

## Introduction

The `alfPrep.R` script loads, combines, and organizes extracted ALFRESCO random variable distributional information from intermediary .RData workspace files produced by upstream **R** scripts in the processing chain.
Curated outputs are saved to **R** workspaces for analysis and graphing by subsequent **R** code.

### Motivation
The primary motivation for this code is not just to extract regional and point data from a large number of high-resolution geotiffs,
but to limit the routine recurrence and redundancy of such extractions.
It allows for storing commonly required data in a more compact format that can be quickly shared and digested by other projects.

### Details

This script uses parallel processing via the base `parallel` package and the function `mclapply`.
Parallel processing is across regions.
Processing is serial across model-scenario pairs.
The code does not make use of `Rmpi` or similar options so it does not take advantage of multi-node cluster parallel processing.
`alfPrep.R` is called via slurm script, `alfPrep.slurm`.

### Files and data
Input files include .RData workspace files storing fire, vegetation, and age data unique to each model, scenario, simulation replicate and spatial region.

The `alfPrep.R` script produces the following curated outputs. Spatially aggregated summary statistics and modeled distributions by region and vegetation class for:

* burn area
* fire frequency
* fire size
* vegetation age
* vegetated cover area

Things to note:
* Age probability distributions have a joint support involving the spatially explicit distribution of ages on the landscape and the variation across the simulation replicates.
* As spatially aggregated statistics by definition, burn area, fire frequency, and vegetation cover probability distributions have a univariate support based strictly on variation across simulation replicates.

## R code

### Setup

```{r setup}
```

### Support functions
Define support functions which assist in assembling curated data frames.

```{r functions1}
```

### Processing function
#### prep_data

```{r prep_data}
```

### Processing

```{r run}
```
