---
title: "ALFRESCO Statistics: Rmpi Code"
output:
  html_document:
    toc: false
    theme: cosmo
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/alfresco/alfStatsByRep_Rmpi.R")
```

## Introduction

The `alfStatsByRep_Rmpi.R` script uses `Rmpi` to efficiently extract fire and vegetation statistics from calibrated, finalized ALFRESCO run output over the full Alaska-Canada 1-km resolution ALFRESCO extent.
Data are saved to **R** workspaces (.RData files) for analysis and graphing by subsequent **R** code.

### Motivation
The primary motivation for this code is not just to extract regional data from a large number of high-resolution geotiffs,
but to limit the routine recurrence and redundancy of such extractions.
It allows for storing commonly required data in a more compact format that can be quickly shared and digested by other projects.

### Details

#### Capabilities
Extractions occur across multiple climate model and scenario-driven runs for multiple simulation replicates.
Statistics are extracted from geotiff output map layers for the entire spatial extent as well as an arbitrary number of spatial subregions.

#### Limitations
This script is intended to run on a single climate model-driven set of ALFRESCO output files at a time; one model-scenario pair.
This is because the outputs for each model-scenario pair consist of 200 simulation replicates.
This is plenty to process at one time.
Scripts further downstream are written with some expectation of this upstream process compiling output statistics based on all replicates,
regardless of how many models or scenarios are processed at once.

### Files and data
The input files include 1-km Alaska-Canada extent data from ALFRESCO simulations
as well as raster layer cell indices pertaining to various regional shapefile polygons.
`alfStatsByRep_Rpmi.R` is called via slurm script, `alfStatsByRep_Rmpi.slurm` and is itself a wrapper around `alfStatsByRep.R` which performs data extractions on multiple CPU cores across multiple compute nodes.

The `alfStatsByRep_Rpmi.R` gathers on a head node the data extracted from ALFRESCO outputs on the CPU cores across all the processing nodes and writes these data to intermediary .RData workspace files:
* Burn area by region
* Fire frequency by region
* Vegetated area by region and vegetation class

Other data are written to files directly by the compute nodes, avoiding returning too much data to the head node.
This consists of distributional information, in contrast to specific computed statistics.

Intermediate outputs are handled by additional **R** scripts.

## R code

### Setup
ADD_TEXT_HERE: EXAMPLE
Setup consists of loading required **R** packages and additional files, preparing any command line arguments for use, and defining functions and other **R** objects.

```{r setup}
```

### Functions
Define support functions.

```{r functions}
```

### Send information from head node to CPUs on compute nodes
Send **R** objects from master to slaves.

```{r obj2slaves}
```

Send **R** commands from master to slaves.

```{r commands2slaves}
```

### Gather data
Extract and compile fire statistics.

```{r fire_stats}
```

Extract and compile vegetation class and age statistics.

```{r age_veg_stats}
```
