---
output:
  html_document:
    toc: false
    theme: cosmo
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/climate/ar4ar5_appcode/appcode_io_sidebar.R")
```

##
##
## SNAP data QA/QC Shiny app R code

`io_main.R` is a server-side **R** script sourced by `app.R`, which is in turn sourced by `server.R`.
It contains a number of reactive outputs rendered in the browser,
specifically outputs which are sent to the sidebar panel area of the app to inform user input controls based on the values of other inputs and outputs.

### io_main.R

#### Panel display, options, and observation

```{r sb_out_01_03}
```

#### Geographic locations

```{r sb_out_04}
```

#### Months to seasons aggregation

```{r sb_out_05_06}
```

#### Decades to longer-term periods aggregation

```{r sb_out_07_08}
```

#### The data subsetting button

```{r sb_out_09}
```

The plot-specific input controls below deal with choice of axis variables, grouping (coloring) variables, faceting variables, and choice of plot subtype or statistic.

#### Time series input controls

```{r sb_out_10_11}
```

#### Scatter plot input controls

```{r sb_out_12_14}
```

#### Heat map input controls

```{r sb_out_15_18}
```

#### Variability plots input controls

```{r sb_out_19_21}
```

#### Distribution plots input controls

```{r sb_out_22_25}
```

#### Vertical faceting and pooled variable text for each plot type

```{r sb_out_26_33}
```

The plot-specific input controls below deal with mainly with aesthetic options such as color palettes, alpha levels, font size, and other aspects of graph display.

#### Time series input controls

```{r sb_out_34_38}
```

#### Scatter plot input controls

```{r sb_out_39_42}
```

#### Heat map input controls

```{r sb_out_43_44}
```

#### Variability plots input controls

```{r sb_out_45_50}
```

#### Distribution plots input controls

```{r sb_out_51_55}
```

#### Conditional plot buttons

These buttons display depending on the current status of data selection and other similarly required non-`NULL`-valued reactive inputs and outputs referenced by the `permitPlot` reactive expression.

```{r sb_out_56_61}
```
