---
output:
  html_document:
    toc: false
    theme: cosmo
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/appcode_reactives.R")
```

##
##
## SNAP data QA/QC Shiny app R code

The `reactives.R` script is sourced by `app.R` which is in turn sourced by `server.R`.
This script contains strict server-side reactive expressions.

### reactives.R

#### Button status

```{r re_01_06}
```

#### Time: months, seasons, years, decades, and long-term periods

```{r re_07_14}
```

#### Models, scenarios, pair logicals, and composites

```{r re_15_22}
```

#### Units, statistics, and bootstrap sample sizes

```{r re_23_28}
```

#### Geographic locations

```{r re_29_32}
```

#### Plot annotations and plot permission check

```{r re_33_43}
```

#### Master GCM data set

```{r re_44}
```

#### Master CRU data set

```{r re_45}
```

#### GCM data subsets

```{r re_46_48}
```

#### CRU data subsets

```{r re_49_50}
```

#### GCM distributions data files

```{r re_51}
```

#### Master GCM distributions data set

```{r re_52}
```

#### Master CRU distributions data set

```{r re_53}
```

The below plot-specific reactive expresssions pertain grouping, faceting, and pooling, and additinal plot settings where applicable.

#### Time series

```{r re_54_58}
```

#### Scatter plot

```{r re_59_63}
```

#### Heat map

```{r re_64_68}
```

#### Variability plots

```{r re_69_75}
```

#### Distribution plots

```{r re_76_82}
```

#### Data aggregation
These reactive expressions perform further data manipulation on input data sets so that summary statistics and aggregated information can be added to a plot.

```{r re_83_87}
```

#### Plot-specific color sequences based on input data

```{r re_89_92}
```
