---
output:
  html_document:
    toc: false
    theme: flatly
    highlight: espresso
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/appcode_app.R")
```

##
##
## SNAP data QA/QC Shiny app R code

The `app.R` script can be viewed as the central hub of the server-side **R** code.
It is sourced by `server.R`.
I keep it externalized because `server.R` also sources `serverHead.R`,
the initial server-side code external to and preceding the `shinyServer` call, which is also a sizeable script on its own.
In turn, `app.R` sources several other **R** scripts as shown below, covering the remainder of the server-side code that flows into `server.R`.
This includes all strict server-side reactive expressions, reactive outputs (assigned specifically to `output` via the `$` operator), and custom `ggplot2`-based plotting functions.

### app.R

#### Source R scripts

```{r app_source}
```

#### Define plot wrapper functions

Each plot function sourced by `app.R` is wrapped in a parent function, which is similarly non-reactive but references known reactive expressions and reactive inputs.

##### Time series wrapper function

```{r app_plotts}
```

##### Scatter plot wrapper function

```{r app_plotsc}
```

##### Heat map wrapper function

```{r app_plothm}
```

##### Variability plots wrapper function

```{r app_plotvr}
```

##### Distribution plots wrapper function

```{r app_plotsp}
```

Outputs below include browser-rendered plots, plot downloads, and data downloads.

#### Time series outputs

```{r app_outts}
```

#### Scatter plot outputs

```{r app_outsc}
```

#### Heat map outputs

```{r app_outvr}
```

#### Variability plots outputs

```{r app_outhm}
```

#### Distribution plots outputs

```{r app_outsp}
```
