---
output:
  html_document:
    toc: false
    theme: united
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/appcode_serverHead.R")
```

##
##
## SNAP data QA/QC Shiny app R code

The `serverHead.R` script is sourced by `server.R` prior to the `shinyServer` call.
It loads required server-side **R** packages and contains numerous support functions used by the app.
A key purpose of including many standard **R** functions here is that many of them are used repeatedly
in order to perform the same operations for different plot types.
While this externalization adds another layer of abstraction to the code,
and while some of these functions clearly serve highly specific purposes and would make no sense without the fuller code context,
it prevents a significant amount of code duplication.

### serverHead.R

#### R packages, themes, colors, and logo

```{r sh_setup}
```

#### nullOrZero
Check if an input is `NULL` or zero.

```{r sh_func01}
```

#### mod2ar
Obtain the AR ID (CMIP phase) based on the climate model.

```{r sh_func02}
```

#### density2bootstrap
Sample from an empirical, estimated probability density function. This is used for distribution plots.

```{r sh_func03}
```

#### splitAt
This function assists `periodLength`.

```{r sh_func04}
```

#### periodLength
This function obtains the length of a defined period (combination of decades) when the user exercises the option to concatenate multiple selected decades into one or more equal-length longer-term periods.

```{r sh_func05}
```

#### collapseMonths
This function aggregates consecutive months into one or more equal-length seasons.

```{r sh_func06}
```

#### periodsFromDecades
This function concatenates decades into one or more equal-length longer-term periods.

```{r sh_func07}
```

#### dodgePoints
This function is used to properly dodge points when points are overlaid on top of other dodged elements such as bars or box plots.
This is necessary when grouping and faceting by categorical values.
`ggplot` is not good at handling this nuance on its own.

```{r sh_func08}
```

#### getHeatmapAxisChoices
This function lists the categorical variables available for use along the axes of a heat map.

```{r sh_func09}
```

#### nGroups
This function returns the number of levels in a cetegorical variable used as the grouping variable.

```{r sh_func10}
```

#### getFacetChoicesHeatmap
This function help control which variables are available for faceting by specifically in a heat map.

```{r sh_func11}
```

#### getFacetPanels
This function returns the number of panels in a plot based on the current faceting variable.

```{r sh_func12}
```

#### getPooledVars
This function obtains a list of currently pooled variables, if any.
It is hierarchically dependent on variables present in the data subset as well as plot settings for which variables are assigned for the x and y axes, grouping, and faceting.
If any variables remain in the data subset, they are known to be pooled.
Additional code attempts to reduce redundancy.
For example, it is pointless to output text which states that data are pooled across both years and decades.

```{r sh_func13}
```

#### getPlotSubTitle
This function provides a "semi-smart" in-panel text annotation based on current plot settings, emphasis on the "semi".

```{r sh_func14}
```

#### getPlotTitle
This function provides a "semi-smart" title to some plots based on current plot settings, emphasis on the "semi".

```{r sh_func15}
```

#### getSubjectChoices
This function handles "subjects" and its result is passed as an input to `withinGroupLines`.

```{r sh_func16}
```

#### adjustGroup
This function handles idiosyncratic combinations of values of grouping variables and its number of factor levels.

```{r sh_func17}
```

#### withinGroupLines
This function controls how lines are drawn in the context of pooled observations.
For example, if there are multiple observations per time point, due to pooling of multiple variables and/or multiple levels of categorical variables,
this function helps ensure that lines are drawn separately for each "subject".

```{r sh_func18}
```

#### scaleColFillMan_prep
`scaleColFillMan_prep` is a support function for `scaleColFillMan`.

```{r sh_func19}
```

#### scaleColFillMan
This function controls and adds `scale_color_manual`, `scale_fill_manual`, `scale_color_brewer`, and/or `scale_fill_brewer` layers to `ggplot` objects.

```{r sh_func20}
```

#### pooledVarsCaption
This function is used to help inform the text output which displays below a plot detailing which, if any, selected variables are pooled together in the plot.

```{r sh_func21}
```

#### getColorSeq
This function returns color sequence options, e.g., qualitative, divergent, etc., based on the number of levels in a selected grouping variable.

```{r sh_func22}
```

#### getColorPalettes
This function returns color palette options based on the available color sequence types.

```{r sh_func23}
```

#### annotatePlot
This function assists with plot annotation.
`annotatePlot` checks whether the x-axiss variable is a factor variable or numeric and attempts to smartly place annotatd text in the graphic panel.
This is not always so easy with `ggplot`.
Furthermore, the text itself, output from `getPlotSubTitle` which attempts to list how certain variables are pooled together in a plot, is only so "smart".
It is worth flagging on to check, but in general I turn this option off just as I tend to turn of the plot title.

```{r sh_func24}
```

#### addLogo
This function assists with adding a `SNAP` logo to a downloaded plot.

```{r sh_func25}
```
