---
title: Code Flow
output:
  html_document:
    toc: false
    theme: flatly
    highlight: espresso
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, echo=FALSE, eval=TRUE, tidy=FALSE, message=FALSE, warning=FALSE)
read_chunk("../../code/code_sankey.R")
```

## Related items
SNAP QAQC code feeds into many other projects, including the SNAP data QAQC master R Shiny app, Community Charts apps, and ALFRESCO-related projects.
The primary order QAQC code is most directly related to data extraction.
Secondary order code relates to organization and preparation of useful data products which are taken up by web applications and other projects to investigate the data.
Tertiary order code relates to specific QAQC analyses.

### Files and Data
This project makes use of any SNAP data, particularly gridded climate, fire, and vegetation data sets.
Files generated as part of SNAP QAQC include fortified datasets which are more accessible, compact, easier to manipulate, understand, and analyze for specific purposes.

### SNAP QAQC code flow

```{r sankey_packages}
```

```{r files}
```

```{r links, tidy=FALSE}
```

```{r igraph}
```

```{r rcharts}
```

```{r code_sankey_embed, comment=NA, results="asis", tidy=F}
```
<style>iframe.rChart{ width: 100%; height: 840px;}</style>
