---
output:
  html_document:
    toc: false
    theme: flatly
    highlight: espresso
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/PRISM_extract.R")
```

##
##
## PRISM 2-km Data Extraction Code

The `PRISM_extract.R` script extracts PRISM 2-km temperature and precipitation data for specific point locations via the raster grid cell in which given spatial coordinates fall.
The extracted values serve as optional historical baseline climatologies for the SNAP Community Charts application.
Use of PRISM values for this purpose has since been superceded by CRU 3.x data.
This script sequentially loads a number of inter-related workspace files containing CRU and GCM data and resaves these workspaces, respectively, under new file names with PRISM data folded into each.

### **R** Code

#### Setup

```{r setup}
```

#### Subset city data

```{r cities}
```

#### Load and save workspaces

```{r save}
```
