---
title: QAQC Shiny App Metadata Finalization
output:
  html_document:
    toc: false
    theme: cosmo
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=FALSE, tidy=TRUE, message=FALSE, warning=FALSE)
read_chunk("../../code/qaqc_app_metadata.R")
```

The `qaqc_app_metadata.R` script loads the `meta.RData` metadata workspace file used by the `cmip3_cmip5` QAQC app.
Final preparations of region and city data file path locations are completed.
This new workspace is saved over the original.

This script current handles subsetting of city files as best it can,
but ultimately time is needed to investigate why GCM and CRU 3.x extractions of the same set of cities (specific grid cells) are yielding different, overlapping sets of cities.

## R code

File path information for GCM and CRU 3.x files are finalized.

```{r regions}
```

File path information for GCM and CRU 3.x cities, and associated metadata, are fortified as best as currently possible.
See code comments for details regarding pending investigation of discrepancies between data sets.

```{r cities}
```

The `meta.RData` workspace used by the master QAQC Shiny app is loaded and re-saved.

```{r save_metadata}
```
