---
output:
  html_document:
    toc: false
    theme: cosmo
    highlight: zenburn
    keep_md: true
---

```{r knitr_setup, echo=FALSE}
opts_chunk$set(cache=FALSE, eval=TRUE, echo=FALSE, tidy=TRUE, messages=FALSE, warnings=FALSE, dpi=300, fig.height=7, fig.width=10.5)
read_chunk("../../code/sp_ac_clump.R")
```

##
##
## Spatial autocorrelation and clump size distributions
The `sp_ac_clump.R` script investigates spatial autocorrelation and clump size distributions of climate variables (currently temperature, single example map) in raster data sets.

### Motivation
High-resolution downscaled data sets may contain high, positive spatial autocorrelation.
In the case of SNAP's downscaled, spatially explicit data sets and other subsequently derived spatially explicit data sets like ALFRESCO output maps,
it is important to investigate the role of spatial autocorrelation with respect to the data:information ratio.

A cursory look at map layers suggests spatial autocorrelation is high virtually everywhere.
Additional considerations include the influence of the underlying high-resolution climatology layer used in downscaling (e.g., PRISM),
which in theory forces essentially the same spatial autocorrelation pattern on every map through time when the map time series being downscaled (e.g., CRU or a GCM)
exists at an incredibly coarse spatial resolution by comparison.

Furthermore, the combination of (1) a typical range in temperature or precipitation levels over the entire spatial extent in a map layer and (2)
the level of precision of the data, ensures that even a map layer containing upwards of a couple million grid cells may be composed of only several hundred unique data values.

Questions of interest include:

*    How does the rate of increase in information content decrease with increasing spatial resolution?
*    How does spatial autocorrelation vary through time, by subregion, and by variable?
*    What effect does spatial autocorrelation have on the sampling distributions of statistics calculated from the data?
*    At what scale should sampling be performed with respect to autocorrelation in the data?
*    What is the degree of spatial clumping of unique values and how are clump sizes distributed, conditional on space and data value?
*    How do clumping, autocorrelation, and a limited set of values relative to the size of a map inform data reduction strategies?

### Initial explorations

### Setup

```{r setup1, eval=FALSE}
```

```{r setup2}
```


#### Autocorrelation and unique observations

```{r autocorr}
```

```{r values}
```

Moran's *I* for this example downscaled temperature map layer is `r round(m_i, 3)` and Geary's *C*, which is inversely related but takes somewhat more into account local autocorrelation, is `r g_c`.
Despite having `r n.dat` grid cells containing data values, there are only `r n` unique values in the entire map, making `r round(1-n/n.dat, 5)*100`% of the map redundant.
A frequency table of just `r n` values would provide a complete description of the probability mass function for the entire unsampled map.

```{r clump_size_plots}
```

Below are four plots examining spatial clump sizes by unique temperature values in the map.
Clumping is typically reserved for discrete data, but considering the precision of the data and range of sensible values over the extent for the given variable,
it is sensible to treat these numeric values as discrete.

#### Scaled cumulative clump size frequency by clump size per temperature value

```{r clump_size_plot1}
```

#### Scaled cumulative clump size frequency by clump size | temperature range

```{r clump_size_plot2}
```

#### Scaled cumulative coverage area by clump size per temperature value

```{r clump_size_plot3}
```

#### Scaled cumulative coverage area by clump size | temperature range

```{r clump_size_plot4}
```

```{r summarize}
```

In the plot below, the marginal distribution of map coverage area by clump size is shown after integrating across all temperature values.
The x-axis is cropped at 100 square km to provide more of a zoomed in view relative to the previous plots since the curve asymptotes fairly quickly thereafter.

#### Scaled cumulative coverage area by clump size < 100 km^2

```{r clump_size_plot5}
```

`r round(p/n.cells, 3)*100`% of data values in the map occur among clumps of identically valued cells while `r round(1-p/n.cells, 3)*100`% of values appear in isolation.
